vocc example

### 2019-08-07 analysis/VOCC/vocc-example.Rmd
Make average (trend-based) vocc work as well and revise plot titles

Choose settings spatial and temporal settings
```{r}
region <- "West Coast Vancouver Island"
trend <- FALSE
start_time <- 2008
end_time <- 2011
```

Choose what variables to base vectors on 
```{r}
# JUST TEMPERATURE
# climate <- "temperature"
# temp_threshold <- c(0.75)
# optimal_temp <- 6.5

# JUST DO
# climate <- "do"
# do_threshold <- c(0.25)
# optimal_do <- 2

# BOTH
climate <- "do and temperature"
max_thresholds <- c(Inf, 0.75)
min_thresholds <- c(0.25, Inf)
optimal_value <- c(2, 6.5)
```

@@

vocc_plot <- plot_vocc(vocc,
  vec_aes = "distance",
  #max_vec_plotted = 100,
  min_vec_plotted = input_cell_size,
  NA_label = ".",
  fill_col = "diff",
  fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  transform_col = no_trans
)
vocc_plot + ggtitle(climate)
}

@@

vocc_plot <- plot_vocc(vocc,
  vec_aes = "distance",
  #max_vec_plotted = 100,
  min_vec_plotted = input_cell_size,
  NA_label = ".",
  fill_col = "diff",
  fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
  raster_alpha = 1,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  vec_alpha = 0.25,
  axis_lables = FALSE,
  transform_col = no_trans
)
vocc_plot + ggtitle(climate)
}

>>>>

Choose settings spatial and temporal settings
```{r}
region <- "West Coast Vancouver Island"
trend <- TRUE # IF TREND will automatically apply different thresholds for average change

# set years if not using an average trend
if (!trend) { 
start_time <- 2008
end_time <- 2011
} 
```

Choose what variables to base vectors on 
```{r}
# JUST TEMPERATURE
climate <- "temperature"
temp_threshold <- c(0.75)
optimal_temp <- 6.5
temp_trend_threshold <- c(0.25)

# # JUST DO
# climate <- "do"
# do_threshold <- c(0.25)
# optimal_do <- 2 
# do_trend_threshold <- c(0.1)

# # BOTH
# climate <- "do and temperature"
# max_thresholds <- c(Inf, 0.75)
# min_thresholds <- c(0.25, Inf)
# optimal_value <- c(2, 6.5) 
# # should be lower than used for raw changes
# min_trend_thresholds <- c(0.1, Inf) 
# max_trend_thresholds <- c(Inf, 0.25)
```

@@

vocc_plot <- plot_vocc(vocc,
  vec_aes = "distance",
  #max_vec_plotted = 100,
  min_vec_plotted = input_cell_size,
  NA_label = ".",
  fill_col = "diff",
  fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  transform_col = no_trans
) + ggtitle(paste("Temperature within", max_thresholds, "°C"))
}

@@

vocc_plot <- plot_vocc(vocc,
  vec_aes = "distance",
  #max_vec_plotted = 100,
  min_vec_plotted = input_cell_size,
  NA_label = ".",
  fill_col = "diff",
  fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
  raster_alpha = 1,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  vec_alpha = 0.25,
  axis_lables = FALSE,
  transform_col = no_trans
) + ggtitle(paste("DO within", min_thresholds, "ml/L") )
}
